Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-31 ms.tex
fixed TDE section

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radio afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}).

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
qualitatively similar to that the density profile we predict for core
galaxies (Fig.~\ref{fig:profiles}, solid line), although to obtain
such a flattening on the inferred radial scale, would require a large
$\Mbh\sim 10^7 \Msun$.  Their inferred gas profile also shows a break
at radii $\sim 0.6$ pc, which in our model corresponds to the break
radius of the galaxy and hence would imply an unrealistically small
SMBH mass $\Mbh\simeq 100\Msun$.  according to the mean relationship
from the \citet{LauerFaber+:2007a} sample. A more likely explanation
is that the observed break in the gas density is associated with a
break in a nuclear star cluster in the galaxy {\bf AGs-ref Carson et
  al. 2015.}.

More detailed models for the environment, and the implications of our
models for CNM profiles for the diversity of radio emission from TDE
jets, will be explored further in future work.

@@

\subsection{Nuclear Star Clusters}

Our results could in principle also have implications for nuclear star clusters or globular clusters.  {\bf BDM :Do we really want to talk about this?  or is this an apology? I will let Aleksey fill in his ideas...}

>>>>

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom+11}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radio afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{BergerZauderer+:2012a}), as shown in Fig.~\ref{fig:bh_growth}.

\citet{BergerZauderer+:2012a} infer a flattening of the gas density
profile of the host of J1644+57 on radial scales $r \gtrsim 0.4$ pc (their Fig.~6) which looks
qualitatively similar to the shape density profile we predict for core
galaxies (Fig.~\ref{fig:profiles}, solid line).  To obtain such a flattening on the inferred radial scales would require a black hole of $\Mbh\sim 10^7 \Msun$.  However,  this is inconsistent with the break in the gas density seen at $\sim 0.6$ pc by \citet{BergerZauderer+:2012a}, which should correspond to the break radius of the {\it stellar density} profile, thus implying an unrealistically small SMBH mass of $\Mbh\simeq 100\Msun$ according to the mean $r_b-M_{\bullet}$ relationship \citep{LauerFaber+:2007a}.  Alternatively, the observed density break in J1644+57 could result from the outer edge of a sub-parsec nuclear star cluster (e.g., \citealt{Carson+15}).  Such compact star clusters could greatly enhance the rate of TDEs (e.g.~\citealt{Stone&Metzger15}), making this association uncoincidental.

%The implications of our model for the CNM profiles of quiescent galaxies on the diversity of radio emission from TDE
%jets will be further developed in future work.

@@
